---
title: "Final paper detail checks and analyses"

author: "Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

The final analyses, comparisons and checks for ***Predicting anxiety, depression and trauma symptoms during the COVID-19 pandemic in the UK***

Note that when GLAD, we always mean GLAD & EDGI 

# Set up 
 
```{r read in data } 
# Read in data
library(tidyverse)
library(data.table)
library(lubridate)
library(psych)


# get file info
source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R")


alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))

```


# Impute and subset data

Impute retrospective scores if no change reported

```{r impute retro}

# impute retro for those who did not change

alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
```


subsample for retro-baseline analysis
exclude those who do not have complete responses for both baseline and retrospective
in addition to those already excluded for NA in age, gender and MH diagnosis.

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Baseline and retrospective data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

dim(dat.retro)
```

subsample for prepan-baseline analysis
exclude those who do not have complete responses for both baseline and prepandemic
in addition to those already excluded for NA in age, gender and MH diagnosis.

PREPANDEMIC
```{r subset prepandemic}

dat.prepan <- alldat %>%
  filter(
    ((data_group_gad == "Prepandemic and baseline data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Prepandemic and baseline data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Prepandemic and baseline data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
  )

dim(dat.prepan)

```


Subset by study

```{r subset by study}

## Subset samples by study

GLAD.prepan <- dat.prepan %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.prepan <- dat.prepan %>%
  filter(Sample == "NBR")

RAMP.prepan <- dat.prepan %>%
  filter(Sample == "RAMP")

### retro
GLAD.retro <- dat.retro %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.retro <- dat.retro %>%
  filter(Sample == "NBR")

RAMP.retro <- dat.retro %>%
  filter(Sample == "RAMP")

```

# Analytic checks and last pass

## Most recent sign up per sample

```{r most recent sign up}

max(RAMP.prepan$startDate.coping)
max(GLAD.prepan$startDate.coping)
max(NBR.prepan$startDate.coping)

```

## Means, SD and n


### overall

Retrospective
```{r means etc overall retro}

vars <- dat.retro %>%
  select(gad.sum_score_base,gad.sum_score_retro,
         phq.sum_score_base,phq.sum_score_retro,
         pcl.sum_score_base)


apply(vars, 2, function(x) list(describe(x)))

```


Prepandemic
```{r means etc overall prepan}

vars <- dat.prepan %>%
  select(gad.sum_score_base,gad.sum_score_prepan,
         phq.sum_score_base,phq.sum_score_prepan,
         pcl.sum_score_base,  pcl.sum_score_prepan)


apply(vars, 2, function(x) list(describe(x)))

```

### By sample

retrospective
```{r means etc by sample retro}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.retro = mean(gad.sum_score_retro, na.rm = TRUE),
            sd.gad.retro = sd(gad.sum_score_retro, na.rm = TRUE),
            n.gad.retro = sum(!is.na(gad.sum_score_retro)),
            
            m.phq.base = mean(phq.sum_score_base, na.rm = TRUE),
            sd.phq.base = sd(phq.sum_score_base, na.rm = TRUE),
            n.phq.base = sum(!is.na(phq.sum_score_base)),
            m.phq.retro = mean(phq.sum_score_retro, na.rm = TRUE),
            sd.phq.retro = sd(phq.sum_score_retro, na.rm = TRUE),
            n.phq.retro = sum(!is.na(phq.sum_score_retro)),
            
            m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE),
            n.pcl.base = sum(!is.na(pcl.sum_score_base)),

            )
```

prepandemic
```{r means etc by sample prepan}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.prepan = mean(gad.sum_score_prepan, na.rm = TRUE),
            sd.gad.prepan = sd(gad.sum_score_prepan, na.rm = TRUE),
            n.gad.prepan = sum(!is.na(gad.sum_score_prepan)),
            
            m.phq.base = mean(phq.sum_score_base, na.rm = TRUE),
            sd.phq.base = sd(phq.sum_score_base, na.rm = TRUE),
            n.phq.base = sum(!is.na(phq.sum_score_base)),
            m.phq.prepan = mean(phq.sum_score_prepan, na.rm = TRUE),
            sd.phq.prepan = sd(phq.sum_score_prepan, na.rm = TRUE),
            n.phq.prepan = sum(!is.na(phq.sum_score_prepan)),
            
            m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE),
            n.pcl.base = sum(!is.na(pcl.sum_score_base)),
            m.pcl.prepan = mean(pcl.sum_score_prepan, na.rm = TRUE),
            sd.pcl.prepan = sd(pcl.sum_score_prepan, na.rm = TRUE),
            n.pcl.prepan = sum(!is.na(pcl.sum_score_prepan)),
            
  )
```



## T tests 

All are Welch's (assuming non equal variances) paired t-tests

### Average scores
Prepandemic
```{r ttest for average scores prepandemic}

t.test(dat.prepan$gad.sum_score_base,dat.prepan$gad.sum_score_prepan, paired = T)
t.test(dat.prepan$phq.sum_score_base,dat.prepan$phq.sum_score_prepan, paired = T)
t.test(dat.prepan$pcl.sum_score_base,dat.prepan$pcl.sum_score_prepan, paired = T)

```

Retrospective
(no retrospective ratings for PCL)
```{r ttest for average scores retrosective}
t.test(dat.retro$gad.sum_score_base,dat.retro$gad.sum_score_retro, paired = T)
t.test(dat.retro$phq.sum_score_base,dat.retro$phq.sum_score_retro, paired = T)
```

### Average scores by sample

Retrospective GAD
```{r ttest average by sample retro gad}

dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)

```


Retrospective PHQ
```{r ttest average by sample retro phq}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$parameter)

```

Prepandemic GAD
```{r ttest average by sample prepan gad}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$parameter)

```

Prepandemic PHQ
```{r ttest average by sample prepan phq}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$parameter)
```

Prepandemic PCL
```{r ttest average by sample prepan pcl}

dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(pcl.sum_score_base,pcl.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$p.value,
         t_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$statistic,
         df = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$parameter)


```
