---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes

params:
  glad.dem.raw: edgi.dem.raw
   
---

This is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

# Specify cohort
```{r}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
```


#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("dplyr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(dplyr)
library(tidyverse)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

#Add_numeric function
Function used to convert character variables into numeric variables. 
```{r add_numeric function}
add_numeric <- function(dat, exclude = NULL) {
  dat_fct <- sjlabelled::as_label(dat)

  dat <- dat[!colnames(dat) %in% exclude]
  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
  return(bind_cols(dat_fct, dat))
}
```

# Data import and merging

Note: GLAD only receives current measures and RAMP questionnaire
Note: All COPING surveys are separate surveys

# Source data file paths 

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```


## GLAD demographics
# Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

# Select variables
```{r glad dem cleaning}
exclude_cols_dem <- c("ID",
                  "Sample",
                  "startDate.glad",
                  "Age_uncleaned",
                  "EduYrs")

glad.dem.raw.id <- glad.dem.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
         startDate.glad, #Date when participant signed up to glad
         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
         Gender = demographics.which_gender_do_you_identify_with, # Gender
         Sex = demographics.select_questionnaire_items_medical, #Sex
         EduYrs = demographics.school_education_school_years.txt, # Years in education
         demographics.college_or_university_degree, # level of education - univeristy
         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
         demographics.cses_or_equivalent, # level of education - cse
         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.dem.raw.id)
# Inspect colnames
colnames(glad.dem.raw.id)
#Differences
dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
```


#Clean Age variable
Age outlier
```{r age outlier}
# define age limits 
age_upper_limit = 117 # oldest person in the world is 117 years
age_lower_limit = 16

# identify number of outliers
length(
  which(
  glad.dem.raw.id$Age_uncleaned > age_upper_limit |
    glad.dem.raw.id$Age_uncleaned < age_lower_limit
     )
)

# remove age outliers
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    Age = 
      if_else(
        Age_uncleaned > age_upper_limit | 
        Age_uncleaned < age_lower_limit, 
        true = NA_real_,
        false = Age_uncleaned,
        missing = NA_real_
      )
  )

# Inspect colnames
colnames(glad.dem.raw.id)
```

# Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {

# Create categorical age groups per 10 years
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ "1",
          Age >= 19 & Age <= 25 ~ "2",
          Age >= 26 & Age <= 35 ~ "3",
          Age >= 36 & Age <= 45 ~ "4",
          Age >= 46 & Age <= 55 ~ "5",
          Age >= 56 & Age <= 65 ~ "6",
          Age >= 66 & Age <= 70 ~ "7",
          Age >= 71 & Age <= 75 ~ "8",
          Age >= 76 & Age <= 80 ~ "9",
          Age >= 81 & Age <= 85 ~ "10",
          Age >= 86 & Age <= 90 ~ "11",
          Age >= 91 & Age <= 100 ~ "12",
          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
                )
      )

glad.dem.raw.id <- glad.dem.raw.id %>%
    mutate(
      age_category =
        recode_factor(
          age_category_numeric, 
          "1" = "16 to 18 years",
          "2" = "19 to 25 years",
          "3" = "26 to 35 years",
          "4" = "36 to 45 years",
          "5" = "46 to 55 years",
          "6" = "56 to 65 years",
          "7" = "66 to 70 years",
          "8" = "71 to 75 years",
          "9" = "76 to 80 years",
          "10" = "81 to 85 years",
          "11" = "86 to 90 years",
          "12" = "91 to 100 years",
          "13" = "Above 100 years"
          )
    )

glad.dem.raw.id %>%
  freq(age_category)

}
```

# Highest education
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education}
#create numeric version of the highest education variable
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        demographics.college_or_university_degree_numeric == "1" ~ 4,
        demographics.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        demographics.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        demographics.cses_or_equivalent_numeric == "1" ~ 1)
    )

#recode the numeric version into a factor
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    highest_education =
      recode_factor(
        highest_education_numeric,
        `1` = "GCSE/CSE",
        `2` = "NVQ",
        `3` = "A-levels",
        `4` = "University")
    )

glad.dem.raw.id %>%
  freq(highest_education)
```

Check highest education coding
```{r Highest education check}
glad.dem.raw.id %>%
  select(highest_education,
        demographics.college_or_university_degree_numeric,
        demographics.a_levelsas_levels_or_equivalent_numeric,
        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric,
        demographics.o_levelsgcses_or_equivalent_numeric,
        demographics.cses_or_equivalent_numeric
  )
```


```{r glad dem head}
head(glad.dem.raw.id)
```


```{r glad dem summary}
summarytools::dfSummary(
  glad.dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad gad

```{r glad gad cols}
glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
dim(glad.gad.raw)
colnames(glad.gad.raw)
```


```{r glad gad cleaning}
exclude_cols <- c("Sample",
                  "ID")

glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.gad.raw.id)
# Inspect colnames
colnames(glad.gad.raw.id)
#Differences
dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
```

Calculate sum score for GAD-7
Max should be 21.

*Note that scores with missingness will be changed to NA later in the script
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_prepan <- c(
  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
  "gad.control_worrying_stop_prepan_numeric",
  "gad.worrying_too_much_about_different_things_prepan_numeric",
  "gad.trouble_relaxing_prepan_numeric",
  "gad.sit_restless_hard_prepan_numeric",
  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
  "gad.awful_feeling_afraid_happen_prepan_numeric"
  )

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = glad.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.gad.raw.id$gad.sum_score_prepan <- gad.scored_items_prepan$scores

# Look at values
glad.gad.raw.id %>%
  descr(gad.sum_score_prepan,
        stats = "common"
        )
```

```{r glad gad head}
head(glad.gad.raw.id)
```

```{r glad gad summary}
summarytools::dfSummary(
  glad.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad mhd

```{r glad mhd cols}
glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
dim(glad.mhd.raw)
colnames(glad.mhd.raw)
```


```{r glad mhd cleaning}
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhd.raw.id)
# Inspect colnames
colnames(glad.mhd.raw.id)
#Differences
dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
```

# Grouping mental health disorders
*#Disorder groupings - from COPING/RAMP analysis minutes*
1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression. The logic for this has been double checked for males - KT/MD. 
2. Anxiety group: generalised anxiety, social anxiety, specific phobia, agoraphobia, panic_disorder, panic_attacks. 
3. Agoraphobia and panic_disorder group: panic_disorder, agoraphobia, panic_attacks.
4. Eating disorders group: anorexianervosa, atypical anorexia nervosa, bulimia nervosa, overeating or bingeeating.
5. Obsessive complusive disorders: obsessive compulaive disorder, obsessive compulsive related disorders. 
6. Psychotic disorders: schizophrenia, schizoaffective disorder, general psychosis or psychotic illness. 
7. Personality disorders: cluster A, cluster B, cluster C
8. Control group: no diagnosed disorders. 

*Disorders of interest*
MDD and other depressive disorders
Anxiety, nerves or generalised anxiety disorder
Social anxiety 
Specific phobia 
Agoraphobia/panic disorder/panic attacks
OCD (& OCD-related disorders e.g., skin picking?)
PTSD 
Bipolar 
Eating disorders (Anorexia, BE-type EDs) 
Personality disorder: Clusters A, B, and C 
No-diagnosis group

*Analysis plan of Disorders: KY and KP analysis plan*
1. Basic: any anxiety or unipolar depressive disorder vs. those with no prior diagnosis
2. Specific: breakdown by type of prior anxiety (& related) disorder diagnosis
3. Breakdown by COVID or not (using COVIDENCE/Zoe algorithm)

```{r glad mhd depressive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depressive_disorders,
       cumul = F)
```

```{r Check depressive_disorders}
glad.mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhd anxiety_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(anxiety_disorders,
       cumul = F)
```

```{r Check anxiety_disorders}
glad.mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhd agoraphobia_panic_disorder}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
glad.mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "2" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
```



Eating disorders group
```{r glad mhd eating_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
```

```{r Check eating_disorders}
glad.mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhd obsessive_compulsive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
glad.mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
```{r glad mhd psychotic_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(psychotic_disorders)
```

```{r Check psychotic_disorders}
glad.mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```

Overlap between self-report schizphrenia and bipolar
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r check bipolar overlap with schizophrenia}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      if_else(
        mhd.schizophrenia_numeric == "1" &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No comorbid bipoar and schizophrenia",
                    "1" = "Comorbid bipoar and schizophrenia",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(bipolar_and_schizophrenia)
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhd personality_cluster_a}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_a =
      recode_factor(personality_cluster_a_numeric,
                    "0" = "No personality disorder cluster A",
                    "1" = "Personality disorder cluster A",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(personality_cluster_a)
```

```{r Check personality_cluster_a}
glad.mhd.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

Cluster B
4. Antisocial                       24 ( 0.8%)
5. Borderline                     2553 (89.4%)
6. Histrionic                        7 ( 0.2%)
7. Narcissistic                      8 ( 0.3%)

```{r glad mhd personality_cluster_b}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_b =
      recode_factor(personality_cluster_b_numeric,
                    "0" = "No personality disorder cluster B",
                    "1" = "Personality disorder cluster B",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(personality_cluster_b)
```

```{r Check personality_cluster_b}
glad.mhd.raw.id %>%
  select(
    personality_cluster_b,
    personality_cluster_b_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

Cluster C
8. Avoidant/anxious                133 ( 4.7%)
9. Dependent                        29 ( 1.0%)
10. Obsessive-compulsive
```{r glad mhd personality_cluster_c}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_c_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_c =
      recode_factor(personality_cluster_c_numeric,
                    "0" = "No personality disorder cluster C",
                    "1" = "Personality disorder cluster C",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(personality_cluster_c)
```

```{r Check personality_cluster_c}
glad.mhd.raw.id %>%
  select(
    personality_cluster_c,
    personality_cluster_c_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

Control grouping
These individuals have no self report diagnosis of any kind that we measure. 
Controls = 784
```{r glad mhd control}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    control =
      recode_factor(control_numeric,
                    "0" = "No control",
                    "1" = "Control",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(control)
```


```{r glad mhd head}
head(glad.mhd.raw.id)
```

```{r glad mhd summary}
summarytools::dfSummary(
  glad.mhd.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r glad mhd categories}
glad.mhd.raw.categories <- glad.mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c
    )
```

# glad pcl

```{r glad pcl cols}
glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
dim(glad.pcl.raw)
colnames(glad.pcl.raw)
```


```{r glad pcl cleaning}
glad.pcl.raw.id <- glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_prepan_numeric = pcl.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_prepan_numeric = pcl.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_prepan_numeric = pcl.stressful_situation_avoiding_activities_numeric,
    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
    pcl.cut_people_feeling_distant_prepan_numeric = pcl.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric = pcl.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_prepan_numeric = pcl.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_prepan = pcl.difficulty_concentrating
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.pcl.raw.id)
# Inspect colnames
colnames(glad.pcl.raw.id)
#Differences
dim(glad.pcl.raw)[1]-dim(glad.pcl.raw.id)[1]
```

Calculate sum score for PCL-6

*Note that scores with missingness will be changed to NA later in the script
```{r pcl sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_prepan <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_prepan <- c(
  "pcl.stressful_experience_repeated_images_prepan_numeric",
  "pcl.stressful_experience_upset_reminded_prepan_numeric",
  "pcl.stressful_situation_avoiding_activities_prepan_numeric",
  "pcl.cut_people_feeling_distant_prepan_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric",
  "pcl.difficulty_concentrating_prepan_numeric"
  )

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = glad.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
glad.pcl.raw.id$pcl.sum_score_prepan <- pcl.scored_items_prepan$scores

# Look at values
glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan,
        stats = "common"
        )
```


```{r glad pcl head}
head(glad.pcl.raw.id)
```

```{r glad pcl summary}
summarytools::dfSummary(
  glad.pcl.raw.id,
  graph.col = F,
  valid.col = F, labels.col = F)
```

# glad phq

```{r glad phq cols}
glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
dim(glad.phq.raw)
colnames(glad.phq.raw)
```


```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_prepan_numeric = phq.little_interest_or_pleasure_in_doing_things_numeric,
    phq.feeling_down_depressed_or_hopeless_prepan_numeric = phq.feeling_down_depressed_or_hopeless_numeric,
    phq.staying_asleep_sleeping_trouble_prepan_numeric = phq.staying_asleep_sleeping_trouble_numeric,
    phq.feeling_tired_or_having_little_energy_prepan_numeric = phq.feeling_tired_or_having_little_energy_numeric,
    phq.poor_appetite_or_overeating_prepan_numeric = phq.poor_appetite_or_overeating_numeric,
    phq.feeling_bad_failure_family_prepan_numeric = phq.feeling_bad_failure_family_numeric,
    phq.trouble_concentrating_reading_newspaper_prepan_numeric = phq.trouble_concentrating_reading_newspaper_numeric,
    phq.moving_fidgety_noticed_opposite_prepan_numeric = phq.moving_fidgety_noticed_opposite_numeric,
    phq.dead_hurting_thoughts_prepan_numeric = phq.dead_hurting_thoughts_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.phq.raw.id)
# Inspect colnames
colnames(glad.phq.raw.id)
#Differences
dim(glad.phq.raw)[1]-dim(glad.phq.raw.id)[1]
```

Calculate sum score for PHQ-9

*Note that scores with missingness will be changed to NA later in the script
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in sum score
phq.items_prepan <- c(
  "phq.little_interest_or_pleasure_in_doing_things_prepan_numeric",
  "phq.feeling_down_depressed_or_hopeless_prepan_numeric",
  "phq.staying_asleep_sleeping_trouble_prepan_numeric",
  "phq.feeling_tired_or_having_little_energy_prepan_numeric",
  "phq.poor_appetite_or_overeating_prepan_numeric",
  "phq.feeling_bad_failure_family_prepan_numeric",
  "phq.trouble_concentrating_reading_newspaper_prepan_numeric",
  "phq.moving_fidgety_noticed_opposite_prepan_numeric",
  "phq.dead_hurting_thoughts_prepan_numeric"
  )

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = glad.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.phq.raw.id$phq.sum_score_prepan <- phq.scored_items_prepan$scores

# Look at values
glad.phq.raw.id %>%
  descr(phq.sum_score_prepan,
        stats = "common"
        )
```

```{r glad phq head}
head(glad.phq.raw.id)
```

```{r glad phq summary}
summarytools::dfSummary(
  glad.phq.raw.id,
  graph.col = F,
  valid.col = F
  )
```


# glad ocir

```{r glad ocir cols}
glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
dim(glad.ocir.raw)
colnames(glad.ocir.raw)
```

```{r glad ocir cleaning}
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
    ocir.arranged_things_prepan = ocir.arranged_things,
    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
    ocir.saved_things_prepan = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.ocir.raw.id)
# Inspect colnames
colnames(glad.ocir.raw.id)
#Differences
dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
```

Calculate sum score for OCI-R

*Note that scores with missingness will be changed to NA later in the script
```{r ocir sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in sum score
ocir.items_prepan = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
  "ocir.arranged_things_change_upset_prepan",
  "ocir.repeat_feel_numbers_prepan",
  "ocir.clean_simply_wash_feel_prepan",
  "ocir.mind_upset_unpleasant_thoughts_prepan",
  "ocir.afraid_avoid_throwing_things_prepan",
  "ocir.light_switches_water_taps_prepan",
  "ocir.arranged_things_prepan",
  "ocir.good_feel_bad_numbers_prepan",
  "ocir.hands_longer_wash_prepan",
  "ocir.saved_things_prepan",
  "ocir.frequently_difficulty_rid_nasty_prepan",
  "ocir.i_check_things_more_often_than_necessary_prepan",
  "ocir.arranged_properly_objects_upset_prepan",
  "ocir.feel_compelled_count_things_prepan",
  "ocir.strangers_touch_touched_difficult_prepan",
  "ocir.control_difficult_find_thoughts_prepan",
  "ocir.i_collect_things_i_dont_need_prepan"
  )

# Calulate sum score
ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
                                        items = glad.ocir.raw.id[ocir.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 4)
# Add in column to tibble
glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores

# Look at values
glad.ocir.raw.id %>%
  descr(ocir.sum_score_prepan,
        stats = "common"
        )
```

```{r glad ocir head}
head(glad.ocir.raw.id)
```

```{r glad ocir summary}
summarytools::dfSummary(
  glad.ocir.raw.id,
  graph.col = F,
  valid.col = F
  )
```

# COPING GLAD: GAD-7

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/gad_coping_glad.rds"))
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

```{r coping glad gad summary}
summarytools::dfSummary(
  coping.glad.gad.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
  )
```


```{r coping glad gad cleaning}
coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.feeling_nervous_anxious_or_on_edge_retro = gad7.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad7.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad7.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad7.trouble_relaxing,
    gad.sit_restless_hard_retro = gad7.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad7.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad7.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad7.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad7.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad7.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad7.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad7.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad7.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad7.awful_feeling_afraid_happen.1,
    gad.feeling_nervous_anxious_or_on_edge_retro_numeric = gad7.feeling_nervous_anxious_or_on_edge_numeric,
    gad.control_worrying_stop_retro_numeric = gad7.control_worrying_stop_numeric,
    gad.worrying_too_much_about_different_things_retro_numeric = gad7.worrying_too_much_about_different_things_numeric,
    gad.trouble_relaxing_retro_numeric = gad7.trouble_relaxing_numeric,
    gad.sit_restless_hard_retro_numeric = gad7.sit_restless_hard_numeric,
    gad.becoming_easily_annoyed_or_irritable_retro_numeric = gad7.becoming_easily_annoyed_or_irritable_numeric,
    gad.awful_feeling_afraid_happen_retro_numeric = gad7.awful_feeling_afraid_happen_numeric,
    gad.feeling_nervous_anxious_or_on_edge_base_numeric = gad7.feeling_nervous_anxious_or_on_edge.1_numeric,
    gad.control_worrying_stop_base_numeric = gad7.control_worrying_stop.1_numeric,
    gad.worrying_too_much_about_different_things_base_numeric = gad7.worrying_too_much_about_different_things.1_numeric,
    gad.trouble_relaxing_base_numeric = gad7.trouble_relaxing.1_numeric,
    gad.sit_restless_hard_base_numeric = gad7.sit_restless_hard.1_numeric,
    gad.becoming_easily_annoyed_or_irritable_base_numeric = gad7.becoming_easily_annoyed_or_irritable.1_numeric,
    gad.awful_feeling_afraid_happen_base_numeric = gad7.awful_feeling_afraid_happen.1_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.gad.raw.id)
# Inspect colnames
colnames(coping.glad.gad.raw.id)
#Differences
dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
```

Calculate sum score for GAD-7 retrospective
```{r coping gad sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_retro <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_retro <- c(
  "gad.feeling_nervous_anxious_or_on_edge_retro_numeric",
  "gad.control_worrying_stop_retro_numeric",
  "gad.worrying_too_much_about_different_things_retro_numeric",
  "gad.trouble_relaxing_retro_numeric",
  "gad.sit_restless_hard_retro_numeric",
  "gad.becoming_easily_annoyed_or_irritable_retro_numeric",
  "gad.awful_feeling_afraid_happen_retro_numeric"
  )

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.glad.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_retro <- gad.scored_items_retro$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro,
        stats = "common"
        )
```

Calculate sum score for GAD-7 baseline
```{r coping gad sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_base <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_base <- c(
  "gad.feeling_nervous_anxious_or_on_edge_base_numeric",
  "gad.control_worrying_stop_base_numeric",
  "gad.worrying_too_much_about_different_things_base_numeric",
  "gad.trouble_relaxing_base_numeric",
  "gad.sit_restless_hard_base_numeric",
  "gad.becoming_easily_annoyed_or_irritable_base_numeric",
  "gad.awful_feeling_afraid_happen_base_numeric"
  )

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.glad.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_base <- gad.scored_items_base$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base,
        stats = "common"
        )
```

```{r coping glad gad head}
head(coping.glad.gad.raw.id)
```

```{r coping glad gad summary 2}
summarytools::dfSummary(
  coping.glad.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# COPING GLAD: PCL-6

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

```{r coping glad pcl summary labels}
summarytools::dfSummary(
  coping.glad.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

Note: Retro for the PCL does not mean retrospective

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
    pcl.difficulty_concentrating_retro = pcl6.difficulty_concentrating.1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.pcl.raw.id)
# Inspect colnames
colnames(coping.glad.pcl.raw.id)
#Differences
dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
```

Calculate sum score for PCL-6 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_retro <- c(
  "pcl.stressful_experience_repeated_images_retro_numeric",
  "pcl.stressful_experience_upset_reminded_retro_numeric",
  "pcl.stressful_situation_avoiding_activities_retro_numeric",
  "pcl.cut_people_feeling_distant_retro_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
  "pcl.difficulty_concentrating_retro_numeric"
)

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_retro <- pcl.scored_items_retro$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro,
        stats = "common"
  )
```


Calculate sum score for PCL-6 base
The sum scores here will not be accurate if we are using complete cases. Only use sum scores here for complete cases, otherwise the minimum will be 0 where it should be 6. 
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_base <- c(
  "pcl.stressful_experience_repeated_images_base_numeric",
  "pcl.stressful_experience_upset_reminded_base_numeric",
  "pcl.stressful_situation_avoiding_activities_base_numeric",
  "pcl.cut_people_feeling_distant_base_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_base_numeric",
  "pcl.difficulty_concentrating_base_numeric"
)

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base,
        stats = "common"
  )
```

```{r coping glad pcl head}
head(coping.glad.pcl.raw.id)
```

```{r coping glad pcl summary}
summarytools::dfSummary(
  coping.glad.pcl.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad COPING phq

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/coping_glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

```{r coping glad phq summary labels}
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```


Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping glad phq cleaning}
coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_retro = phq9.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq9.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq9.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq9.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq9.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq9.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq9.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq9.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro = phq9.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_retro_numeric = phq9.little_interest_or_pleasure_in_doing_things_numeric,
    phq.feeling_down_depressed_or_hopeless_retro_numeric = phq9.feeling_down_depressed_or_hopeless_numeric,
    phq.staying_asleep_sleeping_trouble_retro_numeric = phq9.staying_asleep_sleeping_trouble_numeric,
    phq.feeling_tired_or_having_little_energy_retro_numeric = phq9.feeling_tired_or_having_little_energy_numeric,
    phq.poor_appetite_or_overeating_retro_numeric = phq9.poor_appetite_or_overeating_numeric,
    phq.feeling_bad_failure_family_retro_numeric = phq9.feeling_bad_failure_family_numeric,
    phq.trouble_concentrating_reading_newspaper_retro_numeric = phq9.trouble_concentrating_newspaper_reading_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro_numeric = phq9.moving_fidgety_opposite_slowly_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro_numeric = phq9.dead_hurting_thoughts_numeric,
    phq.little_interest_or_pleasure_in_doing_things_base = phq9.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq9.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq9.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq9.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq9.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq9.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq9.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq9.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base = phq9.dead_hurting_thoughts.1,
    phq.little_interest_or_pleasure_in_doing_things_base_numeric = phq9.little_interest_or_pleasure_in_doing_things.1_numeric,
    phq.feeling_down_depressed_or_hopeless_base_numeric = phq9.feeling_down_depressed_or_hopeless.1_numeric,
    phq.staying_asleep_sleeping_trouble_base_numeric = phq9.staying_asleep_sleeping_trouble.1_numeric,
    phq.feeling_tired_or_having_little_energy_base_numeric = phq9.feeling_tired_or_having_little_energy.1_numeric,
    phq.poor_appetite_or_overeating_base_numeric = phq9.poor_appetite_or_overeating.1_numeric,
    phq.feeling_bad_failure_family_base_numeric = phq9.feeling_bad_failure_family.1_numeric,
    phq.trouble_concentrating_reading_newspaper_base_numeric = phq9.trouble_concentrating_newspaper_reading.1_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base_numeric = phq9.moving_fidgety_opposite_slowly.1_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base_numeric = phq9.dead_hurting_thoughts_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.phq.raw.id)
# Inspect colnames
colnames(coping.glad.phq.raw.id)
#Differences
dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
```

Calculate sum score for PHQ-9 retro
```{r coping phq sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_retro <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
phq.items_retro <- c(
  "phq.little_interest_or_pleasure_in_doing_things_retro_numeric",
"phq.feeling_down_depressed_or_hopeless_retro_numeric",
"phq.staying_asleep_sleeping_trouble_retro_numeric",
"phq.feeling_tired_or_having_little_energy_retro_numeric",
"phq.poor_appetite_or_overeating_retro_numeric",
"phq.feeling_bad_failure_family_retro_numeric",
"phq.trouble_concentrating_reading_newspaper_retro_numeric",
"phq.moving_fidgety_noticed_opposite_retro_numeric",
"phq.dead_hurting_thoughts_retro_numeric"
)

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.glad.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_retro <- phq.scored_items_retro$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro,
        stats = "common"
  )
```

Calculate sum score for PHQ-9 base
```{r coping phq sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_base <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
phq.items_base <- c(
  "phq.little_interest_or_pleasure_in_doing_things_base_numeric",
"phq.feeling_down_depressed_or_hopeless_base_numeric",
"phq.staying_asleep_sleeping_trouble_base_numeric",
"phq.feeling_tired_or_having_little_energy_base_numeric",
"phq.poor_appetite_or_overeating_base_numeric",
"phq.feeling_bad_failure_family_base_numeric",
"phq.trouble_concentrating_reading_newspaper_base_numeric",
"phq.moving_fidgety_noticed_opposite_base_numeric",
"phq.dead_hurting_thoughts_base_numeric"
)

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.glad.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_base <- phq.scored_items_base$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base,
        stats = "common"
  )
```

```{r coping glad phq head}
head(coping.glad.phq.raw.id)
```

```{r coping glad phq summary}
summarytools::dfSummary(
  coping.glad.phq.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad COPING ocir

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

```{r coping glad ocir summary labels}
summarytools::dfSummary(
  coping.glad.ocir.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
```{r coping glad ocir cleaning}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
  drop_na(recipientFirstName) %>% # Drop NAs
  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
    ocir.arranged_things_retro = ocir.arranged_things,
    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
    ocir.saved_things_retro = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
    ocir.arranged_things_base = ocir.arranged_things.1,
    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
    ocir.saved_things_base = ocir.saved_things.1,
    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.ocir.raw.id)
# Inspect colnames
colnames(coping.glad.ocir.raw.id)
#Differences
dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
```

Calculate sum score for OCI-R retro
```{r coping ocir sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
ocir.items_retro = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
  "ocir.arranged_things_change_upset_retro",
  "ocir.repeat_feel_numbers_retro",
  "ocir.clean_simply_wash_feel_retro",
  "ocir.mind_upset_unpleasant_thoughts_retro",
  "ocir.afraid_avoid_throwing_things_retro",
  "ocir.light_switches_water_taps_retro",
  "ocir.arranged_things_retro",
  "ocir.good_feel_bad_numbers_retro",
  "ocir.hands_longer_wash_retro",
  "ocir.saved_things_retro",
  "ocir.frequently_difficulty_rid_nasty_retro",
  "ocir.i_check_things_more_often_than_necessary_retro",
  "ocir.arranged_properly_objects_upset_retro",
  "ocir.feel_compelled_count_things_retro",
  "ocir.strangers_touch_touched_difficult_retro",
  "ocir.control_difficult_find_thoughts_retro",
  "ocir.i_collect_things_i_dont_need_retro"
)

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro,
        stats = "common"
  )
```

Calculate sum score for OCI-R base
```{r coping ocir sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
ocir.items_base = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
  "ocir.arranged_things_change_upset_base",
  "ocir.repeat_feel_numbers_base",
  "ocir.clean_simply_wash_feel_base",
  "ocir.mind_upset_unpleasant_thoughts_base",
  "ocir.afraid_avoid_throwing_things_base",
  "ocir.light_switches_water_taps_base",
  "ocir.arranged_things_base",
  "ocir.good_feel_bad_numbers_base",
  "ocir.hands_longer_wash_base",
  "ocir.saved_things_base",
  "ocir.frequently_difficulty_rid_nasty_base",
  "ocir.i_check_things_more_often_than_necessary_base",
  "ocir.arranged_properly_objects_upset_base",
  "ocir.feel_compelled_count_things_base",
  "ocir.strangers_touch_touched_difficult_base",
  "ocir.control_difficult_find_thoughts_base",
  "ocir.i_collect_things_i_dont_need_base"
)

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base,
        stats = "common"
  )
```

```{r coping glad ocir head}
head(coping.glad.ocir.raw.id)
```

```{r coping glad ocir summary}
summarytools::dfSummary(
  coping.glad.ocir.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# Join tibbles together

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhd.raw.categories,
  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id,
  coping.glad.ocir.raw.id
)
```


```{r Join all questionnaires for glad}
dat.glad.raw <- plyr::join_all(
  glad.dfs.list,
  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
  )

#look at the data
skimr::skim(dat.glad.raw)
```

Check duplicates again to be saved
+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
+++KT: No duplicates identified by ID in GLAD. 
```{r glad Check duplicates}
dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)

summary(as.factor(dat.glad.raw$ID.dup))

dat.dup <- dat.glad.raw %>%
  filter(ID.dup == TRUE)

dat.glad.raw.no.dup <- dat.glad.raw %>%
  filter(ID.dup == FALSE)
```

#Exclusion
Exclude those without sex, gender, age and incomplete PHQ/GAD items
Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
```{r Exclude participants that do not report sex}
dim(dat.glad.raw)
dat.no.sex <- dat.glad.raw %>%
  drop_na(Sex)
dim(dat.no.sex)

dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
```
`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex


```{r Exclude participants that do not report gender}
dim(dat.no.sex)
dat.no.sex.no.gender <- dat.no.sex %>%
  drop_na(Gender)
dim(dat.no.sex.no.gender)

dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
```
`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex


```{r Exclude participants that do not report age}
dim(dat.no.sex.no.gender)
dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
  drop_na(age_category)
dim(dat.no.sex.no.gender.no.age)

dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
```
`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age

Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
```{r COVID exclusion of IBD}
#dim(dat.no.sex.no.age)
#
#dat.no.sex.no.age <- dat.no.sex.no.age %>%
#  filter(NBR.IBD == 0)
#
#dim(dat.no.sex.no.age.no.ibd)
#
#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
```

##Missingness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count and percentages
```{r PHQ baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
           %in%
             phq.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_base = 
      na_per_person_phq_base/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
```

```{r PHQ baseline missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.base_cut_off = 
      if_else(
        na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
```


#PHQ - retrospective
PHQ Missingness NAs per person - count and percentages
```{r PHQ retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
           %in%
             phq.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_retro = 
      na_per_person_phq_retro/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
```


```{r PHQ retro missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.retro_cut_off = 
      if_else(
        na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
```

#PHQ - prepandemic
PHQ Missingness NAs per person - count and percentages
```{r PHQ prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
           %in%
             phq.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_prepan = 
      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
```


```{r PHQ prepan missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.prepan_cut_off = 
      if_else(
        na_per_person_phq_prepan == 1 & 
          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
```

Count for PHQ baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for PHQ}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
```


#GAD - baseline
GAD Missingness NAs per person - count and percentages
```{r gad baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
           %in%
             gad.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_base = 
      na_per_person_gad_base/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
```

#GAD - retrospective
GAD Missingness NAs per person - count and percentages
```{r gad retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
           %in%
             gad.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_retro = 
      na_per_person_gad_retro/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
```

#GAD - prepandemic
GAD Missingness NAs per person - count and percentages
```{r gad prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_gad_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
           %in%
             gad.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_gad_prepan = 
      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
```

Count for gad baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for gad}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
```


#PCL - baseline
PCL Missingness NAs per person - count and percentages
```{r pcl baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_pcl_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at baseline
           %in%
             pcl.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_pcl_base = 
      na_per_person_pcl_base/6 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_base)
```

#PCL - retrospective
PCL Missingness NAs per person - count and percentages
```{r pcl retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_pcl_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at retroline
           %in%
             pcl.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_pcl_retro = 
      na_per_person_pcl_retro/6 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_retro)
```

#PCL - prepandemic
pcl Missingness NAs per person - count and percentages
```{r pcl prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_pcl_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
           %in%
             pcl.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_pcl_prepan = 
      na_per_person_pcl_prepan/6 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_prepan)
```

Count for pcl baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for pcl}
# baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
# retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
# pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)

# rename dataset
dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
```


#OCI-R - baseline
OCI-R Missingness NAs per person - count and percentages
```{r OCI-R baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_ocir_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at baseline
           %in%
             ocir.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_ocir_base = 
      na_per_person_ocir_base/18 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_base)
```

#OCI-R - retrospective
OCI-R Missingness NAs per person - count and percentages
```{r OCI-R retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_ocir_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at retroline
           %in%
             ocir.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_ocir_retro = 
      na_per_person_ocir_retro/18 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_retro)
```

#OCI-R - prepandemic
OCI-R Missingness NAs per person - count and percentages
```{r OCI-R prepan missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_ocir_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at prepanline
           %in%
             ocir.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan) #have a look at the frequency 

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_ocir_prepan = 
      na_per_person_ocir_prepan/18 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_prepan)
```

Count for OCI-R baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for OCI-R}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan)
```

#Sum scores missingness cut offs
KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL. 

PHQ
The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
```{r sum score cut offs PHQ base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_base_full =
      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
              NA_real_,
              phq.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
```

```{r sum score cut offs PHQ prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_prepan_full =
      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
              NA_real_,
              phq.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
```

```{r sum score cut offs PHQ retro}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_retro_full =
      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
              NA_real_,
              phq.sum_score_retro
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
```

GAD
The GAD sum score is set to NA if they have any missing items
```{r sum score cut offs GAD base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_base_full =
      if_else(na_per_person_gad_base > 0,
              NA_real_,
              gad.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
```

```{r sum score cut offs GAD prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_prepan_full =
      if_else(na_per_person_gad_prepan > 0,
              NA_real_,
              gad.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
```

```{r sum score cut offs GAD retro}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    gad.sum_score_retro_full =
      if_else(na_per_person_gad_retro > 0,
              NA_real_,
              gad.sum_score_retro
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
```

PCL
The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
```{r sum score cut offs PCL base}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    pcl.sum_score_base_full =
      if_else(na_per_person_pcl_base > 0,
              NA_real_,
              pcl.sum_score_base
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
```

```{r sum score cut offs PCL prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    pcl.sum_score_prepan_full =
      if_else(na_per_person_pcl_prepan > 0,
              NA_real_,
              pcl.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
```



##Create tidy data on which the exclusion criteria have been applied
Complete sex, gender, age and missingness information applied. 
```{r Tidy data}
dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness

skimr::skim(dat.glad)
```

# Definition of prepandemic and baseline 
Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th. 

Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)

Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*

Baseline = COPING/RAMP sign up questionnaire

Dates for the definition of prepandemic
```{r Potential dates for prepandemic definition}
# Date of the first COVID-19 case in the United Kingdom (UK)
date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")

# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")

# Date the UK went into lockdown
date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
```


```{r Prepandemic definitions january_31}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_january_31_numeric =
      if_else(
        startDate.glad > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_january_31 =
      recode_factor(
        prepandemic_january_31_numeric,
        "0" = "Sign up after 31. January",
        "1" = "Sign up before 31. January"
      )
  )

dat.glad %>%
  freq(prepandemic_january_31)
```


```{r Prepandemic definitions march_1}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_1_numeric =
      if_else(
        startDate.glad > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_1 =
      recode_factor(
        prepandemic_march_1_numeric,
        "0" = "Sign up after 1. March",
        "1" = "Sign up before 1. March"
      )
  )

dat.glad %>%
  freq(prepandemic_march_1)
```

```{r Prepandemic definitions march_23}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_23_numeric =
      if_else(
        startDate.glad > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_23 =
      recode_factor(
        prepandemic_march_23_numeric,
        "0" = "Sign up after 23. March",
        "1" = "Sign up before 23. March"
      )
  )

dat.glad %>%
  freq(prepandemic_march_23)
```

Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
```{r time difference between sign up questionnaire and COPING questionnaire}
dat.glad <- dat.glad %>%
  mutate(
    time_diff_sign_up_coping =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping.glad,    #should be start date for COPING (time1)
          startDate.glad),    #should be start date for GLAD (time2)
          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

dat.glad %>%
  descr(
    var = time_diff_sign_up_coping,
    stats = "common"
    )
```

Proportion of people signed up over one year ago
```{r eval=FALSE, include=FALSE}
dat.glad <- dat.glad %>%
  mutate(
    over_one_year_time_diff_sign_up_coping_numeric =
      as.numeric(
        if_else(time_diff_sign_up_coping > 365, 1, 0
                )
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    over_one_year_time_diff_sign_up_coping =
      recode_factor(
        over_one_year_time_diff_sign_up_coping_numeric,
        "0" = "Sign up under one year before COPING",
        "1" = "Sign up over one year before COPING"
      )
  )

table(dat.glad$over_one_year_time_diff_sign_up_coping)
```

#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
PHQ difference scores
```{r phq difference scores}
# Difference score for prepandemic and retrospective phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_retro =
      as.numeric(
        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$phq.diff_score_prepan_retro)

# Difference score for prepandemic and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_base =
      as.numeric(
        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$phq.diff_score_prepan_base)

# Difference score for retrospective and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_base_retro =
      as.numeric(
        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$phq.diff_score_base_retro)

```

GAD difference scores
```{r gad difference scores}
# Difference score for prepandemic and retrospective gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_retro =
      as.numeric(
        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$gad.diff_score_prepan_retro)

# Difference score for prepandemic and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_base =
      as.numeric(
        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$gad.diff_score_prepan_base)

# Difference score for retrospective and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_base_retro =
      as.numeric(
        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$gad.diff_score_base_retro)

```

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
# Difference score for prepandemic and baseline pcl sum scores
dat.glad <- dat.glad %>%
  mutate(
    pcl.diff_score_prepan_base =
      as.numeric(
        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$pcl.diff_score_prepan_base)
```

```{r frequency of those who reported "due to pandemic" in retro PCL}
summary(dat.glad$pcl.sum_score_retro)

freq(dat.glad$pcl.stressful_experience_repeated_images_retro)
freq(dat.glad$pcl.stressful_situation_avoiding_activities_retro)
freq(dat.glad$pcl.feeling_irritable_or_having_angry_outbursts_retro)
freq(dat.glad$pcl.stressful_experience_upset_reminded_retro)
freq(dat.glad$pcl.cut_people_feeling_distant_retro)
freq(dat.glad$pcl.difficulty_concentrating_retro)
```

OCI-R difference scores
```{r ocir difference scores}
# Difference score for prepandemic and retrospective oci-r sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_prepan_retro =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$ocir.diff_score_prepan_retro)

# Difference score for prepandemic and baseline ocir sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_prepan_base =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

summary(dat.glad$ocir.diff_score_prepan_base)

# Difference score for retrospective and baseline ocir sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_base_retro =
      as.numeric(
        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$ocir.diff_score_base_retro)

```

#Data level groups
Identify which data (prepan, retro and baseline) each participant has.
```{r data level groups PHQ}
dat.glad <- dat.glad %>%
  mutate(
    data_group_phq_numeric =
      case_when(
        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_phq = 
      recode_factor(
        data_group_phq_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )


table(dat.glad$data_group_phq)
```



GAD
```{r data level groups GAD}
dat.glad <- dat.glad %>%
  mutate(
    data_group_gad_numeric =
      case_when(
        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_gad = 
      recode_factor(
        data_group_gad_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_gad)
```

PCL
```{r data level groups PCL}
dat.glad <- dat.glad %>%
  mutate(
    data_group_pcl_numeric =
      case_when(
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_pcl = 
      recode_factor(
        data_group_pcl_numeric,
        "0" = "Only prepandemic data",
        "1" = "Baseline and retrospective data",
        "2" = "Prepandemic and baseline data",
        "3" = "Baseline data only",
        "4" = "Retrospective data only",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_pcl)
```


#Read in respiratory data
```{r coping resp cols}
coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/respiratory_coping_glad.rds"))
dim(coping.glad.respiratory.raw)
colnames(coping.glad.respiratory.raw)
```


Select respiratory variables
```{r read in respiratory data}
coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID,
    respiratory.breath_diarrhoea_fatigue_fever,
    respiratory.worst_ill_feel,
    respiratory.persistent_cough,
    respiratory.skipping_meals_because_you_felt_unwell,
    respiratory.was_your_sense_of_smell_impaired,
    respiratory.was_your_sense_of_taste_impaired,
    respiratory.feeling_tiredfatigued,
    respiratory.throat_swab_coronavirus_nose,
    respiratory.throat_swab_test_nose,
    respiratory.coronavirus_antibody_test,
    respiratory.results_antibody_test
    # ID
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.respiratory.raw.id)
# Inspect colnames
colnames(coping.glad.respiratory.raw.id)
#Differences
dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]

```

```{r create respiratory numeric variables}
exclude_cols <- c("ID",
                  "Sample")

coping.glad.respiratory.raw.numeric <- add_numeric(coping.glad.respiratory.raw.id, exclude = exclude_cols)

colnames(coping.glad.respiratory.raw.numeric)
dim(coping.glad.respiratory.raw.numeric)
dim(coping.glad.respiratory.raw.id)
```

#Distribution of likert scale COVID-19 symptoms in COPING
```{r distribution of COVID symptoms}
#persistent cough
coping.glad.respiratory.raw.numeric %>%
  ggplot(
    mapping = aes(
      y = respiratory.persistent_cough_numeric 
    )
  ) +
  geom_bar() +
  labs(
    title = "Persistant cough"
  )

#severe fatigue
coping.glad.respiratory.raw.numeric %>%
  ggplot(
    mapping = aes(
        y = respiratory.feeling_tiredfatigued_numeric 
    )
  ) +
  geom_bar() +
  labs(
    title = "Severe fatigue"
  )

#skipped meals
coping.glad.respiratory.raw.numeric %>%
  ggplot(
    mapping = aes(
        y = respiratory.skipping_meals_because_you_felt_unwell_numeric
    )
  ) +
  geom_bar() +
  labs(
    title = "Skipped meals"
  )

```

#Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
Coding:
0 = No symptoms
1 = Mild symptoms
2 = Moderate symptoms
3 = Severe symptoms

Results:
Persistent cough: "Mild symptoms" as cut off
Fatigue: "Severe symptoms" as cut off
Skipped meals: "Moderate symptoms" as cut off
```{r proportion of people who report COVID symptoms in Menni et al}
#persistent cough
percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
quantile(x = coping.glad.respiratory.raw.numeric$respiratory.persistent_cough_numeric, 
         na.rm = TRUE, 
         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response

#fatigue
percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
quantile(x = coping.glad.respiratory.raw.numeric$respiratory.feeling_tiredfatigued_numeric, 
         na.rm = TRUE, 
         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response

#skipped meals 
percentage_skipped_meals <- ((0.4203*6452) + (0.2493*9186) + (0.1912*2434931))/(6452+9186+2434931) 
percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
quantile(x = coping.glad.respiratory.raw.numeric$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
         na.rm = TRUE, 
         probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
```

Creating binary groups for COVID symptoms
```{r creating binary groups for COVID symptoms}
#loss or smell or taste
coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
  mutate(
    respiratory.anosmia_binary =
      if_else(
        respiratory.was_your_sense_of_smell_impaired_numeric == 1 | respiratory.was_your_sense_of_taste_impaired_numeric == 1, 
        1,
        0
      )
  )

#persistent cough
coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
  mutate(
    respiratory.pcough_binary =
      if_else(
        respiratory.persistent_cough_numeric >= 1, #those who score 1 or above (mild or above)
        1,
        0
      )
  )

#fatigue
coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
  mutate(
    respiratory.fatigue_binary =
      if_else(
        respiratory.feeling_tiredfatigued_numeric >= 3, #those who score 3 (severe symptoms)
        1,
        0
      )
  )

#skipped meals
coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
  mutate(
    respiratory.skipped_meals_binary =
      if_else(
        respiratory.skipping_meals_because_you_felt_unwell_numeric >= 2,
        1,
        0
      )
  )
```

Frequencies of binary COVID symptoms
```{r frequencies of COVID binary symptoms}
freq(coping.glad.respiratory.raw.numeric$respiratory.anosmia_binary)
freq(coping.glad.respiratory.raw.numeric$respiratory.pcough_binary)
freq(coping.glad.respiratory.raw.numeric$respiratory.fatigue_binary)
freq(coping.glad.respiratory.raw.numeric$respiratory.skipped_meals_binary)
```

Rename respiratory dataset joined to main dataset
```{r clean respiratory dataset}
coping.glad.respiratory <- coping.glad.respiratory.raw.numeric

dat.glad.coping <- left_join(
  x = dat.glad,
  y = coping.glad.respiratory,
  by = "ID"
)
```

# Probable COVID-19 case identification
Algorithm from Menni et al. to identify probable COVID-19
Variables required:
- Sex: 	0 Female, 1 Male
- Other binary variables: 0 No, 1 Yes       
- "respiratory.anosmia_binary": loss of smell or taste  
- "respiratory.pcough_binary":	Persistent cough
- "respiratory.fatigue_binary": Severe fatigue
- "respiratory.skipped_meals_binary": Skipped meals

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING

```{r create numeric sex variable with male=1}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        1,
        0
      )
  )
```

```{r how many people expereinced all symptoms}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    people_with_symptoms =
      if_else(
          !is.na(respiratory.anosmia_binary) &
          !is.na(respiratory.pcough_binary) &
          !is.na(respiratory.fatigue_binary) &
          !is.na(respiratory.skipped_meals_binary),
        1,
        0
       )
  )

table(dat.glad.coping$people_with_symptoms)
```


```{r COVID prediction model}
# linear model of covid symptoms
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

# Calcualte the odds ratios 
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_odds_ratio = 
      (exp(covid_probability) / (1 + exp(covid_probability)))
  )

# generate binary cutt off variable for risk of COVID 
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )
		  )
		      
#create factor with labels
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_odds_ratio_50 =
      recode_factor(
        covid_odds_ratio_50_numeric,
        "0" = "No COVID",
        "1" = "Probable COVID"
      )
  )

#frequency table for covid variables 
covid_variables <- c("covid_odds_ratio",
                      "covid_probability"
                    )

descr(x = dat.glad.coping[,covid_variables],
      round.digits = 2,
      transpose = TRUE)

## looking at cases over 0.5
freq(dat.glad.coping$covid_odds_ratio_50, 
     cumul = FALSE) 
```












