---
title: "PANCHANGE_analysis"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("eeptools")
#install.packages("skimr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(broom)
library(tidyverse)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```


# Data import

## Source data file paths 

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```


### Read in data
```{r read in data}
dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat)
colnames(dat)
```

Filter data frame to exclude participants that never answered COPING
```{r}

```



```{r Vectors with diff_score_cols}
diff_score_cols <- dat %>%
  select(contains("diff_score")) %>% 
  colnames()

diff_score_cols

phq.diff_score_cols <- dat %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

phq.diff_score_cols

gad.diff_score_cols <- dat %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

gad.diff_score_cols

ocir.diff_score_cols <- dat %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

ocir.diff_score_cols
```



```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

Data availability
```{r gad availability}
dat %>%
  freq(
    data_group_gad,
    cumul = F)
```

```{r phq availability}
dat %>%
  freq(
    data_group_phq,
    cumul = F)
```

```{r pcl availability}
dat %>%
  freq(
    data_group_pcl,
    cumul = F)
```

Data availability OCI-R
```{r}

```

Descriptives of age
```{r}

```


```{r vector with psychiatric disorders}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric",
    "control_numeric"
)
```



```{r gather to long format Disorder}
dat.long <- dat %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder,
    Diagnosis
  )

head(dat.long)
```

Define disorder columns in vector

```{r Disorder by Gender}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Gender) %>%
  count(Disorder)
```



```{r Disorder by Sample}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Sample) %>%
  count(Disorder)
```

Ethnicity should be recoded
European
Mixed or multiple ethnic origins
African or African British
Asian or Asian British
Arab
```{r Disorder by Ethnicity}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Ethnicity) %>%
  count(Disorder)
```


Compare the GLAD/EDGI and COPING cohorts as a whole
+++CH: Diagnosis, ethnicity, gender, 
+++MD: May not be possible for NBR; potentially send them code to run it for us

Ethnicity
```{r}
dat %>%
  group_by(Ethnicity, Sample) %>%
  count(Ethnicity)
```


Gender
```{r}
dat %>%
  group_by(Gender, Sample) %>%
  count(Gender)
```

highest_education
```{r}
dat %>%
  group_by(highest_education, Sample) %>%
  count(highest_education)
```

Key worker status
```{r}
dat %>%
  group_by(key_worker, Sample) %>%
  count(key_worker)
```

COVID test positive
```{r}
dat %>%
  group_by(respiratory.throat_swab_test_nose, Sample) %>%
  count(respiratory.throat_swab_test_nose)
```

```{r}
dat %>%
  group_by(respiratory.results_antibody_test, Sample) %>%
  count(respiratory.results_antibody_test)
```


COVID probable diagnosis
```{r}
dat %>%
  group_by(covid_probable_case_incl_screening, Sample) %>%
  count(covid_probable_case_incl_screening)
```



```{r gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

head(dat.long.gad.diff)
```

makes this into percentages
```{r}
dat.long.gad.diff %>%
  ggplot(mapping = aes(y = gad.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

```{r gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw) %>%
  drop_na(phq.diff_score)

head(dat.long.phq.diff)
```


```{r}
dat.long.phq.diff %>%
  filter(Time_point != "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
   geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
    ) +
  theme_minimal()
```

```{r}
dat.long.phq.diff %>%
  filter(Time_point == "prepan_retro") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
   geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
    ) +
  theme_minimal()
```




```{r gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

head(dat.long.ocir.diff)
```

```{r}
dat.long.ocir.diff %>%
  ggplot(mapping = aes(y = ocir.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```


```{r}
gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_retro_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
  geom_bar() +
  theme_minimal()

gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar() +
  theme_minimal()

```

```{r fig.height=5, fig.width=5}
gad.diff_score_prepan_base_plot /
  gad.diff_score_prepan_retro_plot /
  gad.diff_score_prepan_base_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```


Calculate mean change per disorder group 
Disorders (9) 
Sex 
Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed) 

```{r}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder) %>%
  summarise(
    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T),
    ocir_base_retro = mean(ocir.diff_score_base_retro, na.rm = T),
    ocir_prepan_retro = mean(ocir.diff_score_prepan_retro, na.rm = T),
    ocir_prepan_base = mean(ocir.diff_score_prepan_base, na.rm = T)
    )
```


Rank the disorders by the size of the change 


# Regression
Regress covariates out of the change? Which? 

Model 0: Disorders
```{r}
model0 <- lm(
  formula = gad.diff_score_base_retro ~ Disorder,
  data = dat.long)

summary(model0)
```

```{r}
tidy(model0)
```

```{r}
model1 <- lm(
  formula = gad.diff_score_base_retro ~ time_diff_sign_up_coping,
  data = dat)

summary(model1)
```



Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = gad.diff_score_base_retro ~ Gender + Age + Ethnicity + time_diff_sign_up_coping + Sample,
  data = dat)

summary(model1)
```


Re-calculate change
```{r}

```


Re-rank the change again
```{r}

```


PCL:  
Calculate the total GLAD, COPING, RAMP baseline 
```{r}

```


For each item 
present percentages of how say that this is due to the pandemic 
```{r}

```


Calculate a variable PCL pandemic score 
```{r}

```


If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis 
```{r}

```

 


Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
+++KLP: Discuss during the meeting if we use 3 or 5 categories
```{r}

```


Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
```{r}

```


```{r}

```

