---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: "14/07/2020"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This will be the master script to run all analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
Set up the Rmarkdown
+++CH: Add packages for the setup
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date
to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(tidyverse)
library(psych)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
+++CH: Is there a document in which these colours are defined?
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette=COPINGpalette2
```



#Stratify descriptives by mental health diagnosis
 *convert diagnostic columns from wide to long format*
 +++CH: May not be necessary if the data is already in long form
```{r COVID change to long format}
###ADAPT TO CORRECT VARIABLE NAMES
dat.long <- dat.wide %>%
  gather(key = "time", value = "score", all_of(PHQ.variables)) %>% #this will be all diagnostic variables
  convert_as_factor(ID, time)
```

## Disorders - Frequencies *use this as example to convert chunk above*
```{r Disorders - Frequencies}
#0 = No to disorder; 1 = Yes to disorder
PMAD_na_drop_Dx %>%
  select(ID, #need to add columns for which you want summaries for - ASK GB & KY what they want in descriptives table
         dem.sex,
         starts_with("mhd.") & ends_with("numeric")) %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
  ) %>%
  group_by(Disorder) %>%
  count(Diagnosis) #count for diagnoses
```



Calculate the time difference between the sign up month (GLAD) and pandemic measures (COPING)
***KT: NEED TO HAVE START DATE IN DATASET TO RUN THESE
```{r time difference between GLAD and COPING completion KATIE}
##IGNORE - only for testing if the date formats work 
dat <- ramp.dem.raw #start date has been removed so had to test it this way
dat$test.date <- as.POSIXct("2020-05-15") 

#change naming of variables here based on what we decide for "startDate"
dat$date.diff.glad <- round( 
                      difftime(           #this function does time1 - time2 as difftime(time1, time2...)
                        dat$test.date,    #should be start date for COPING (time1)
                        dat$startDate,    #should be start date for GLAD (time2)
                        units = c("days"  #can also be "secs", "mins", "hours", "weeks"
                                  ))) 
freq(dat$date_diff.glad)        
```

Calculate the time difference between the sign up month (EDGI) and pandemic measures (COPING)
```{r time difference between EDGI and COPING completion KATIE}
#change naming of variables here based on what we decide for "startDate"
dat$date.diff.edgi <- round( 
                      difftime(           #this function does time1 - time2 as difftime(time1, time2...)
                        dat$test.date,    #should be start date for COPING (time1)
                        dat$startDate,    #should be start date for EDGI (time2)
                        units = c("days"  #can also be "secs", "mins", "hours", "weeks"
                                  ))) 
freq(dat$date_diff.edgi)      
```


Compare the GLAD/EDGI and COPING cohorts as a whole
+++CH: Diagnosis, ethnicity, gender, 
+++MD: May not be possible for NBR; potentially send them code to run it for us
```{r}

```



Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
+++KLP: Discuss during the meeting if we use 3 or 5 categories
```{r}

```

##Calculate difference pre and baseline
For individuals who have objective scores for GAD, PHQ and PCL. Subtract the baseline from the pre pandemic. Plot this distribution. If they have a higher score at baseline than pre-pandemic, the difference would be positive and would indicate that the participant got worse. 

```{r COVID calculate the difference between pre and post}

```

Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
```{r}

```










