---
title: "PANCHANGE_analysis"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("eeptools")
#install.packages("skimr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(eeptools) # Needed to calculate age from birthdate
library(tidyverse)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```


# Data import

## Source data file paths 

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```


### Read in data
```{r read in data}
dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat)
colnames(dat)
```

```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

Data availability
```{r gad availability}
dat %>%
  freq(
    data_group_gad,
    cumul = F)
```

```{r phq availability}
dat %>%
  freq(
    data_group_phq,
    cumul = F)
```

```{r pcl availability}
dat %>%
  freq(
    data_group_pcl,
    cumul = F)
```