---
title: "PANCHANGE_analysis_backup"
author: "Christopher Huebel"
date: "18/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### CHANGE SCORES

### GAD

```{r GAD prepan Model 0a}
# Model
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)

# Regression statistics
gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0a_reg_stats)
gad_prepan_model0a_reg_stats

# Estimate summary table
gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a, conf.int = TRUE) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "95% CI low" = format(
      round(conf.low,
            digits = 2),
      nsmall = 2),
    "95% CI up" = format(
      round(conf.high,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "95% CI low",
    "95% CI up",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0a_estimates)
gad_prepan_model0a_estimates
```


```{r GAD prepan Model 0b}
gad_prepan_model0b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)


# Regression statistics
gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0b_reg_stats)
gad_prepan_model0b_reg_stats

# Estimate summary table
gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
      "depressive_disordersDepressive disorder" = "Depressive disorders",
      "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
      "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
      "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
      "eating_disordersEating disorder" = "Eating disorders",
      "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
      "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
      "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
      "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
      "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
      "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
      "mhd.personality_disorderPersonality disorder" = "Personality disorder"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0b_estimates)
gad_prepan_model0b_estimates
```


```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)

# Regression statistics
gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model1a_reg_stats)
gad_prepan_model1a_reg_stats

# Estimate summary table
gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
      "Gender_collapsedFemale" = "Female",
      "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
      "age_category_collapsed19-25" = "19-25 years",
      "age_category_collapsed26-35" = "26-35 years",
      "age_category_collapsed36-45" = "36-45 years",
      "age_category_collapsed46-55" = "46-55 years",
      "age_category_collapsed56-65" = "56-65 years",
      "age_category_collapsed66-70" = "66-70 years",
      "age_category_collapsed71-75" = "71-75 years",
      "age_category_collapsed76+" = "76+ years",
      "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
      "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
      "Ethnicity_collapsedAfrican or African British" = "African or African British",
      "Ethnicity_collapsedOther" = "Other ethnicity",
      "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
    #    "z score",
    "p value"
  )

kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model 0a}
phq_prepan_model0a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model 0b}
phq_prepan_model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```


### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(ocir_prepan_model0b)
tidy(ocir_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1a)
tidy(ocir_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1b)
tidy(ocir_prepan_model1b)
```

### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model absolute values absolute values 0a}
gad_prepan_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)
tidy(gad_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD prepan Model absolute values 0b}
gad_prepan_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)
tidy(gad_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1a}
gad_prepan_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)
tidy(gad_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1b}
gad_prepan_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model absolute values 0a}
phq_prepan_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model absolute values 0b}
phq_prepan_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1a}
phq_prepan_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1b}
phq_prepan_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```


### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model absolute values 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model absolute values 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model absolute values 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model absolute values 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(ocir_prepan_model0b)
tidy(ocir_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1a)
tidy(ocir_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1b)
tidy(ocir_prepan_model1b)
```



## Retro-baseline change

### CHANGE SCORES

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model 0a}
gad_retro_model0a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(gad_retro_model0a)
tidy(gad_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model 0b}
gad_retro_model0b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(gad_retro_model0b)
tidy(gad_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1a}
gad_retro_model1a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1a)
tidy(gad_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1b)
tidy(gad_retro_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model 0a}
phq_retro_model0a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(phq_retro_model0a)
tidy(phq_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model 0b}
phq_retro_model0b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(phq_retro_model0b)
tidy(phq_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1a}
phq_retro_model1a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1a)
tidy(phq_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1b}
phq_retro_model1b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1b)
tidy(phq_retro_model1b)
```


### PCL

++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.

```{r recode PCL retro variable as numeric}
dat.retro <- dat.retro %>% 
  mutate(
    pcl.sum_score_retro = 
      as.numeric(pcl.sum_score_retro_raw)
  )
```

Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(pcl_retro_model0a)
tidy(pcl_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(pcl_retro_model0b)
tidy(pcl_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1a)
tidy(pcl_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1b)
tidy(pcl_retro_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model 0a}
ocir_retro_model0a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(ocir_retro_model0a)
tidy(ocir_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model 0b}
ocir_retro_model0b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(ocir_retro_model0b)
tidy(ocir_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1a}
ocir_retro_model1a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1a)
tidy(ocir_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1b}
ocir_retro_model1b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1b)
tidy(ocir_retro_model1b)
```



### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model absolute values 0a}
gad_retro_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(gad_retro_model0a)
tidy(gad_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model absolute values 0b}
gad_retro_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(gad_retro_model0b)
tidy(gad_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1a}
gad_retro_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1a)
tidy(gad_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1b}
gad_retro_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1b)
tidy(gad_retro_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model absolute values 0a}
phq_retro_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(phq_retro_model0a)
tidy(phq_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model absolute values 0b}
phq_retro_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(phq_retro_model0b)
tidy(phq_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1a}
phq_retro_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1a)
tidy(phq_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1b}
phq_retro_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1b)
tidy(phq_retro_model1b)
```


### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model absolute values 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(pcl_retro_model0a)
tidy(pcl_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model absolute values 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(pcl_retro_model0b)
tidy(pcl_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1a)
tidy(pcl_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1b)
tidy(pcl_retro_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model absolute values 0a}
ocir_retro_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(ocir_retro_model0a)
tidy(ocir_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model absolute values 0b}
ocir_retro_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(ocir_retro_model0b)
tidy(ocir_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1a}
ocir_retro_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1a)
tidy(ocir_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1b}
ocir_retro_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1b)
tidy(ocir_retro_model1b)
```



# RUBBISH

+++ Everything underneath here is only SCRATCH

```{r RUBBISH 2, fig.height=7, fig.width=5}
#gad.diff_score_base_prepan_plot /
#  gad.diff_score_retro_prepan_plot /
#  gad.diff_score_base_retro_plot +
#  plot_layout(guides = "collect", heights = c(1,1,1)) +
#  plot_annotation(tag_levels = "A")
```


